% coding: utf-8
% --------------------------------------------------------------------------------------------------
% "Параметризация стабилизирующих управлений в стохастических системах с непрерывным временем", 2009
% : список литературы
% --------------------------------------------------------------------------------------------------

\addcontentsline{toc}{chapter}{Список использованной литературы}

\begin{thebibliography}{wlab}

\bibitem{TROF}
\emph{Crusius C.\,A.\,R., Trofino A}.
\newblock Sufficient LMI Conditions for Output Feedback Control Problems.
\newblock IEEE Trans. Automat. Control. 1999. V. 44. P. 1053–1057.

\bibitem{CDC}
\emph{Peaucelle D., Pakshin P.}
\newblock LQR parametrization of static output feedback gains for linear systems with Markovian switching and related robust stabilization and passification problems.

\bibitem{RUS}
\emph{Pakshin P., Solovyev S., Peaucelle D.}
\newblock Parametrization of stabilizing controllers for stochastic systems.

\bibitem{BOYD}
\emph{Boyd S., Ghaoui L.\,E., Feron E., Balakrishnan V.}
\newblock Linear Matrix Inequalities in System and Control Theory.
\newblock SIAM studies in applied mathematics; vol. 15, ISBN 0-89871-334-X, 1994.

\bibitem{CRUSIUS}
\emph{Crusius C.\,A.\,R.}
\newblock Formulac\~{a}o LMI para problemas de performance e robustez.
\newblock Master’s dissertation, Universidade Federal de Santa Catarina, EEL/UFSC Florian\'{o}polis, Brasil, 1996.

\bibitem{PERES}
\emph{Peres P.\,L.\,D., Geromel J.\,C., Souza S.\,R.}
\newblock Optimal $\mathcal{H}_2$ control by output feedback.
\newblock in \emph{Proc. Conf. Decision and Control}, Dec. 1993, pp. 102–107.

\bibitem{GLXKA}
\emph{Gadewadikar J., Lewis F.\,L., Xie L., Kucera V., Abu-Khalaf M.}
\newblock Parametrization of all stabilizing static state-feedback gains: Application to output-feedback design
\newblock Automatica, Vol.43. pp. 1597 - 1604, 2007.

\pagebreak

\bibitem{KM}
\emph{Kats I.\,Ya., Martynyk A.\,A.}
\newblock Stability and stabilization of nonlinear systems with random structures.
\newblock Taylor and Francis, London, 2002.

\bibitem{SIG}
\emph{Skeleton R.\,E., Iwasaki T., Grigoriadis K.\,M.}
\newblock A unified algebraic approach to linear control design.
\newblock Taylor and Francis, London, 1997.

\bibitem{PF}
\emph{Peaucelle D., Fradkov A.}
\newblock LMI conditions for robust adaptive control of LTI systems.
\newblock In \emph{IFAC Workshop on Adaptation and Learning in Control and Signal Processing}, St. Petersburg, August 2007. Paper
in \emph{Invited Session ''Passification-based Adaptive and Robust Control``}.

\bibitem{YAKUBOVICH}
\emph{Якубович В.\,А.}
\newblock Решение некоторых матричных неравенств, встречающихся в теории автоматического регулирования.
\newblock ДАН СССР. 1962. Т. 143 №6, с. 1304-1307

\bibitem{FRADKOV}
\emph{Фрадков А.\,Л., Андриевский Б.\,Р.}
\newblock Метод пассификации в задачах адаптивного управления, оценивания и синхронизации.
\newblock Автоматика и телемеханика, 2006. №11, С. 3-37.



\end{thebibliography}
